A Generalized Reduced Linear Program for Markov Decision Processes

### 2016-07-08 single/lubp.tex
Chandru's shortened version

%!TEX root =  autocontgrlp.tex
\section{Least Upper Bound Projection}\label{sec:lubp}
Let $e_j$ denote the $j$th basis vector in the standard Euclidean bases of $\R^n$.
We make the following assumption on $\N$:
\begin{assumption}
\label{ass:n}
The set $\N$ satisfies the following conditions:
\begin{enumerate}[(i)]
\item \label{ass:n1}
For any $t\in \R$, $t e_1 + \N \eqdef \{ r + t e_1 \,:\, r\in \N \} = \N$, i.e., 
$\N$ is invariant to shifts by vectors of the form $t e_1$.
\item \label{ass:n2}
For $2\le i \le k$, $\sup_{r\in \N} | e_i^\top r | <+\infty$.
\item \label{ass:n3}
For each $1\le i \le n$, there exists a solution $r_i\in \R^k$ to the ALP \eqref{alp} with $c = e_i$ such that
$r_i\in \N$.
\item \label{ass:n4}
For each $1\le i \le n$, there exists a solution $r_i\in \R^k$ to the GRLP \eqref{grlp} with $c = e_i$ such that
$r_i\in \N$.
\end{enumerate}
\end{assumption}
Recalling that the first column vector of $\Phi$ is $\one$, \eqref{ass:n1} implies that $\{\Phi r \,:\,r\in \N \}$ is invariant to shifts by constants, a property that will prove to be useful.
Part~\eqref{ass:n2} is required to guarantee that solutions to the LPs we define below are bounded.
To satisfy \eqref{ass:n2}, \eqref{ass:n3} and \eqref{ass:n4} 
simultaneously, it is enough to select $\N$ to be contained in 
$\{ r = (r_1,\dots,r_k)^\top \in \R^k \,:\, \max_{2\le i \le k} |r_i| \le r_{\max} \}$ with $r_{\max}>0$ sufficiently large.
\todoc{Can we calculate an a priori bound on how $r_{\max}$ should be? It is a major weakness if we cannot
suggest a way to define $\N$.}

@@

 \underset{r\in \R^k}{\min} &\,\, c^\top \Phi r\,,\\
 \text{s.t.}& \mb \Phi r\geq  TJ\,, \qquad r\in \N\,.

@@

@@

We now show that $\Gamma$ is a contraction. 
By \cref{maxnorm}, it suffices to show that $\Gamma$ is monotone and linear along $[\one]$-rays with a factor smaller than one.
We start with monotonicity.
\begin{lemma}\label{gmonotone}
For $J_1, J_2\in \R^n$ such that $J_1\leq J_2$, we have $\Gamma J_1\leq \Gamma J_2$.
\end{lemma}
\begin{proof}
Choose any $i\in \{1,\ldots,n\}$. 
Since $J_1\leq J_2$, we have $TJ_1\leq TJ_2$.
Hence, $\F_{J_2} \subset \F_{J_1}$ and thus $(\Gamma J_1)(i) \le (\Gamma J_2)(i)$. 
Since $i$ was arbitrary, the result follows.
\end{proof}
\begin{lemma}\label{lpsol}
Let $A\in \R^{u\times v}$, $b,c\in \R^u$ and $b_0=Ax_0$ for 
some $x_0 \in \R^v$, $\N \subset \R^v$ such that $\N =x_0+ \N$. Then
\begin{align}
\min\{c^\top Ax:Ax\geq b+b_0, x\in \N\} =\min\{c^\top A y:Ay \geq b, y \in \N \}+c^\top b_0.
\end{align}
\end{lemma}
\begin{proof}
The claim follows by the change of variables $y := x-x_0$.
\end{proof}
\begin{lemma}\label{gshift}
Let $J\in \R^n$ and $t\in \R$ be a constant.
Then, $\Gamma (J+t\one) = \Gamma J + \alpha t \one$.
\end{lemma}
\begin{proof}
Consider the $i^{th}$ linear programs associated with $\Gamma J$ and $\Gamma (J+ t\one)$. 
The result follows by using Lemma~\ref{lpsol} with $A=\Phi$, $b=TJ$, $c=e_i$, $b_0=\alpha t\mathbf{1}$ 
and $x_0=\alpha t e_1$, noting that thanks to
\cref{one}, $A x_0 = b_0$ and that thanks to
\cref{ass:n} \eqref{ass:n1}, $\N = \N + \alpha t e_1$.
\end{proof}
\begin{theorem}\label{gmaxcontra}
The operator $\Gamma  \colon \R^n\ra \R^n$ obeys the $\max$-norm contraction property with factor $\alpha$.
\end{theorem}
\begin{proof}
The statement follows immediately from Lemmas~\ref{gmonotone} and~\ref{gshift}, and \cref{maxnorm}.
\end{proof}
\if0
\begin{corollary}
Let $V_0$ be arbitrary and $(V_n)$ be defined recursively by
\begin{align}\label{pvi}
V_{n+1}&=\Gamma V_n, \quad n\geq 0\,.
\end{align}
Then, $V_n$ converges to the the unique fixed point $\tv$ of $\Gamma$.
\end{corollary}
\fi
Define $\tv$ denote the unique fixed point of $\Gamma$.
\todoc{I am mildly unhappy with denoting the fixed point of $\Gamma$ by $\tv$, but much happier with denoting
the fixed point of $\hg$ by $\hv$. So this is progress:)}
\begin{lemma}\label{gfp}
The vector $\tv$ obeys $\tv\geq T\tv$.
\end{lemma}
\begin{proof}
From the definitions we have $\tv(i) = (\Gamma \tv)(i) = (\Phi r_{e_i,\tv})(i) \ge (T\tv)(i)$, $1\le i \le n$.
\if0
Consider the $i^{th}$ linear program associated with $\Gamma \tv$. We know that $\Phi r_{e_i}\geq T \tv$, for all $i=1,\ldots, n$. The result follows from noting that $\tv$ is the unique fixed point of $\Gamma $ and that $\tv(i)=(\Phi r_{e_i,V})(i)$.
\fi
\end{proof}
Recall that $\tj$ denotes the solution to the ALP in \eqref{alp}.
The fixed point of $\Gamma$ is sandwiched between $J^*$ and $\tj$:
\begin{lemma}\label{relation1}
%Assume that $\N$ is such that if $r_i$ is
%the solution to the ALP in \eqref{alp} for $c=e_i$ then $r_i\in \N$, $1\le i \le n$.
% $\tv$, the unique fixed point of the iterative scheme \eqref{pvi}, and the solution $\tj$ to the ALP in \eqref{alp}, obey 
The relation $\tj\geq\tv\geq J^*$ holds.
\end{lemma}
\begin{proof}
Since $\tv\geq T\tv$ it follows that $\tv\geq J^*$. 
Let $r_1, r_2,\ldots, r_n$ be solutions to the ALP in \eqref{alp} for $c=e_1, e_2,\ldots,e_n$ respectively
such that $r_1,\dots,r_n\in \N$. It is possible to find such solutions thanks to \cref{ass:n} \eqref{ass:n3}.
Define $V_0\in \R^n$ by $V_0(i)=\underset{j=1,\ldots, n}{\min}(\Phi r_j)(i)$, $1\le i \le n$. 
It is clear from the definition of $V_0$ that $\tj(i), \Phi r_j(i) \geq\Phi r_i(i)\geq V_0(i)$, $1\le i,j \le n$. 
Also from the monotone property of $T$, we have $T\Phi r_j\geq T V_0$,
hence, by the definition of $r_j$ we also have,
$\Phi r_j\geq T\Phi r_j \geq T V_0$, 
and so by taking component-wise minimum,
$V_0 \geq T V_0$.

Now let $V_{n+1} = \Gamma V_n$, $n=0,1,\dots$. Then, $V_1(i) = (\Gamma V_0)(i) = \min\{ V(i) \,:\, V\in \F_{V_0} \}
\le \min\{ V(i) \,:\, V\ge V_0, V = \Phi r, r\in \N \} \le \min\{ V(i)\,:\, V \ge V_0, V = \Phi r_j, 1\le j \le n \} = V_0(i)$,
where in the last step we used that $r_1,\dots,r_n \in \N$.
Hence, $V_1 \le V_0$. Using the monotone property of $\Gamma$ (i.e., \cref{gmonotone})
we then get $V_{n+1}\le V_n$ for $n\ge 0$ and thus 
$\tj\geq V_0\geq V_1\ldots\geq \tv \geq J^*$.
\end{proof}
\input{perfbnds}

>>>>

%!TEX root =  autocontgrlp.tex
\section{Least Upper Bound Projection}\label{sec:lubp}
Let $e_j$ denote the $j$th basis vector in the standard Euclidean bases of $\R^n$.
We make the following assumption on $\N$:
\begin{assumption}
\label{ass:n}
The set $\N$ satisfies the following conditions:
\begin{enumerate}[(i)]
\item \label{ass:n1}
For any $t\in \R$, $t e_1 + \N \eqdef \{ r + t e_1 \,:\, r\in \N \} = \N$, i.e., 
$\N$ is invariant to shifts by vectors of the form $t e_1$.
\item \label{ass:n2}
For $2\le i \le k$, $\sup_{r\in \N} | e_i^\top r | <+\infty$.
\item \label{ass:n3}
For each $1\le i \le n$, there exists a solution $r_i\in \R^k$ to the ALP \eqref{alp} with $c = e_i$ such that
$r_i\in \N$.
\item \label{ass:n4}
For each $1\le i \le n$, there exists a solution $r_i\in \R^k$ to the GRLP \eqref{grlp} with $c = e_i$ such that
$r_i\in \N$.
\end{assumption}
Recalling that the first column vector of $\Phi$ is $\one$, \eqref{ass:n1} implies that $\{\Phi r \,:\,r\in \N \}$ is invariant to shifts by constants, a property that will prove to be useful.
Part~\eqref{ass:n2} is required to guarantee that solutions to the LPs we define below are bounded.
To satisfy \eqref{ass:n2}, \eqref{ass:n3} and \eqref{ass:n4} 
simultaneously, it is enough to select $\N$ to be contained in 
$\{ r = (r_1,\dots,r_k)^\top \in \R^k \,:\, \max_{2\le i \le k} |r_i| \le r_{\max} \}$ with $r_{\max}>0$ sufficiently large.
\todoc{Can we calculate an a priori bound on how $r_{\max}$ should be? It is a major weakness if we cannot
suggest a way to define $\N$.}

@@

 \underset{r\in \N'}{\min} &\,\, c^\top \Phi r\,,\\
 \text{s.t.}& \mb \Phi r\geq  TJ.

@@

\begin{definition}\label{alubpop}
Given $J\in \R^n$ and the nonnegative valued vector $c\in \R^n_+$, define $r'_{c,J}'$ to be the solution to 
\begin{align}\label{alubplp}
 \underset{r\in \N'}{\min}& \,\mb c^\top \Phi r\,,\nn\\
 \text{s.t.}& \,\,\, W^\top E \Phi r\geq W^\top HJ.
Then, for $J\in \R^n$, $\hg J$, the approximate least upper bound (ALUB) projection of $J$ is defined as 
\begin{align}\label{tgamdef}
(\hg J)(i)\eqdef(\Phi \har_{e_i,J})(i), \mb i=1,\ldots,n\,.

@@

\begin{comment}
We now show that $\Gamma$ is a contraction. 
By \cref{maxnorm}, it suffices to show that $\Gamma$ is monotone and linear along $[\one]$-rays with a factor smaller than one.
We start with monotonicity.
\begin{lemma}\label{gmonotone}
For $J_1, J_2\in \R^n$ such that $J_1\leq J_2$, we have $\Gamma J_1\leq \Gamma J_2$.
\end{lemma}
\begin{proof}
Choose any $i\in \{1,\ldots,n\}$. 
Since $J_1\leq J_2$, we have $TJ_1\leq TJ_2$.
Hence, $\F_{J_2} \subset \F_{J_1}$ and thus $(\Gamma J_1)(i) \le (\Gamma J_2)(i)$. 
Since $i$ was arbitrary, the result follows.
\end{proof}
\begin{lemma}\label{lpsol}
Let $A\in \R^{u\times v}$, $b,c\in \R^u$ and $b_0=Ax_0$ for 
some $x_0 \in \R^v$, $\N \subset \R^v$ such that $\N =x_0+ \N$. Then
\begin{align}
\min\{c^\top Ax:Ax\geq b+b_0, x\in \N\} =\min\{c^\top A y:Ay \geq b, y \in \N \}+c^\top b_0.
\end{align}
\end{lemma}
\begin{proof}
The claim follows by the change of variables $y := x-x_0$.
\end{proof}
\begin{lemma}\label{gshift}
Let $J\in \R^n$ and $t\in \R$ be a constant.
Then, $\Gamma (J+t\one) = \Gamma J + \alpha t \one$.
\end{lemma}
\begin{proof}
Consider the $i^{th}$ linear programs associated with $\Gamma J$ and $\Gamma (J+ t\one)$. 
The result follows by using Lemma~\ref{lpsol} with $A=\Phi$, $b=TJ$, $c=e_i$, $b_0=\alpha t\mathbf{1}$ 
and $x_0=\alpha t e_1$, noting that thanks to
\cref{one}, $A x_0 = b_0$ and that thanks to
\cref{ass:n} \eqref{ass:n1}, $\N = \N + \alpha t e_1$.
\end{proof}
\begin{theorem}\label{gmaxcontra}
The operator $\Gamma  \colon \R^n\ra \R^n$ obeys the $\max$-norm contraction property with factor $\alpha$.
\end{theorem}
\begin{proof}
The statement follows immediately from Lemmas~\ref{gmonotone} and~\ref{gshift}, and \cref{maxnorm}.
\end{proof}
\if0
\begin{corollary}
Let $V_0$ be arbitrary and $(V_n)$ be defined recursively by
\begin{align}\label{pvi}
V_{n+1}&=\Gamma V_n, \quad n\geq 0\,.
\end{align}
Then, $V_n$ converges to the the unique fixed point $\tv$ of $\Gamma$.
\end{corollary}
\fi
Define $\tv$ denote the unique fixed point of $\Gamma$.
\todoc{I am mildly unhappy with denoting the fixed point of $\Gamma$ by $\tv$, but much happier with denoting
the fixed point of $\hg$ by $\hv$. So this is progress:)}
\begin{lemma}\label{gfp}
The vector $\tv$ obeys $\tv\geq T\tv$.
\end{lemma}
\begin{proof}
From the definitions we have $\tv(i) = (\Gamma \tv)(i) = (\Phi r_{e_i,\tv})(i) \ge (T\tv)(i)$, $1\le i \le n$.
\if0
Consider the $i^{th}$ linear program associated with $\Gamma \tv$. We know that $\Phi r_{e_i}\geq T \tv$, for all $i=1,\ldots, n$. The result follows from noting that $\tv$ is the unique fixed point of $\Gamma $ and that $\tv(i)=(\Phi r_{e_i,V})(i)$.
\fi
\end{proof}
Recall that $\tj$ denotes the solution to the ALP in \eqref{alp}.
The fixed point of $\Gamma$ is sandwiched between $J^*$ and $\tj$:
\begin{lemma}\label{relation1}
%Assume that $\N$ is such that if $r_i$ is
%the solution to the ALP in \eqref{alp} for $c=e_i$ then $r_i\in \N$, $1\le i \le n$.
% $\tv$, the unique fixed point of the iterative scheme \eqref{pvi}, and the solution $\tj$ to the ALP in \eqref{alp}, obey 
The relation $\tj\geq\tv\geq J^*$ holds.
\end{lemma}
\begin{proof}
Since $\tv\geq T\tv$ it follows that $\tv\geq J^*$. 
Let $r_1, r_2,\ldots, r_n$ be solutions to the ALP in \eqref{alp} for $c=e_1, e_2,\ldots,e_n$ respectively
such that $r_1,\dots,r_n\in \N$. It is possible to find such solutions thanks to \cref{ass:n} \eqref{ass:n3}.
Define $V_0\in \R^n$ by $V_0(i)=\underset{j=1,\ldots, n}{\min}(\Phi r_j)(i)$, $1\le i \le n$. 
It is clear from the definition of $V_0$ that $\tj(i), \Phi r_j(i) \geq\Phi r_i(i)\geq V_0(i)$, $1\le i,j \le n$. 
Also from the monotone property of $T$, we have $T\Phi r_j\geq T V_0$,
hence, by the definition of $r_j$ we also have,
$\Phi r_j\geq T\Phi r_j \geq T V_0$, 
and so by taking component-wise minimum,
$V_0 \geq T V_0$.

Now let $V_{n+1} = \Gamma V_n$, $n=0,1,\dots$. Then, $V_1(i) = (\Gamma V_0)(i) = \min\{ V(i) \,:\, V\in \F_{V_0} \}
\le \min\{ V(i) \,:\, V\ge V_0, V = \Phi r, r\in \N \} \le \min\{ V(i)\,:\, V \ge V_0, V = \Phi r_j, 1\le j \le n \} = V_0(i)$,
where in the last step we used that $r_1,\dots,r_n \in \N$.
Hence, $V_1 \le V_0$. Using the monotone property of $\Gamma$ (i.e., \cref{gmonotone})
we then get $V_{n+1}\le V_n$ for $n\ge 0$ and thus 
$\tj\geq V_0\geq V_1\ldots\geq \tv \geq J^*$.
\end{proof}
\input{perfbnds}
\end{comment}

### 2016-07-08 single/mdpshort.tex
Chandru's shortened version

\section{Introduction}
Optimal sequential decision making problems occurring in science, engineering and economics can be cast in the framework of Markov Decision Processes (MDPs). We consider MDPs with large but finite number of states, i.e., $S=\{1,2,\ldots,n\}$ for some large $n$, and the action set is given by $A=\{1,2,\ldots,d\}$. For simplicity, we assume that all actions are feasible in all states. The probability transition kernel $P$ specifies the probability $p_a(s,s')$ of transitioning from state $s$ to state $s'$ under the action $a$. We denote the reward obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.\par

@@

where $\alpha \in (0,1)$ is a given discount factor. Here $J_u(s)$ is known as the value of the state $s$ under the SDP $u$, and the vector quantity $J_u\stackrel{\Delta}{=}(J_u(s), \forall s\in S)\in R^n$ is called the value-function corresponding to the SDP $u$. The \emph{optimal policy} $u^*$ is obtained as $u^*(s)\stackrel{\Delta}{=}\arg\max_{u\in U}J_u(s)$\footnote{Such $u^*$ exists and is well defined in the case of infinite horizon discounted reward MDP, for more details see \cite{Puter}.}, where $U$ is the class of all SDPs. The \emph{optimal value-function} $J^*$ is the one obtained under the optimal policy, i.e., $J^*=J_{u^*}$.\par
Any optimal policy $u^*$ and the value function $J^*$ obey the Bellman equation (BE): for all $ s \in S$, 
\begin{subequations}\label{bell}
\label{bellval}J^*(s)&=\max_{ a\in A}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big),\\
\label{bellpol}u^*(s)&= \underset{a\in A}{\argmax}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big)\,.
\end{subequations}
If $J^*$ is computed first, then $u^*$ can be obtained via \eqref{bellpol}. Thus computing the value function is at the heart of most solution methods to MDP.
The optimal value function $J^*$ can be obtained by solving the following linear program :

@@

\text{s.t.}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'),\nn\\
&\forall s \in S, a \in A,

@@

where $c$ is a probability distribution such that $c(s)>0, \forall s \in S$ and $\sum_{s\in S}c(s)=1$.

@@

We now define certain important quantities which will used in the rest of the paper.

@@

\item The greedy policy with respect to the value function $\tj$ as \begin{align*}\tu\eqdef\underset{a\in A}{\argmax}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')\tj(s')\big)\end{align*}

@@

When the MDP has a large number of states it is difficult to solve for $J^*$, using either the linear program \eqref{mdplp} or other full state representation methods such as value iteration, policy iteration \cite{BertB}. A practical solution is to resort to function approximation. The most widely used is the linear function approximation wherein the exact value function is approximated by a function that is obtained as a linear combination of a set of pre-selected basis functions.

>>>>

\section{Markov Decision Processes (MDPs)}
%In this section, we briefly discuss the basics of Markov Decision Processes (MDPs) (the reader is referred to \cite{BertB,Puter} for a detailed treatment).\\
%Optimal sequential decision making problems occurring in science, engineering and economics can be cast in the framework of Markov Decision Processes (MDPs), where the problem is to find a policy $u$, mapping states to actions, so as to maximize long term expected cumulated discounted reward. A given policy $u$ is associated with a value function $J_u$ (a mapping from the state space to the set of reals\footnote{Also known as reward/cost-to-go function.}), which gives the value of each state under a given policy $u$. The optimal value function $J^*$ collects the highest values achievable in each state. A policy $u^*$ is optimal if it achieves the optimal value in each state, i.e., if $J^* = J_{u^*}$. 
In this section, briefly discuss the basics of Markov Decision Processes (MDPs) (the reader is referred to \cite{BertB,Puter} for a detailed treatment).\\
We consider MDPs with large but finite number of states, i.e., $S=\{1,2,\ldots,n\}$ for some large $n$, and the action set is given by $A=\{1,2,\ldots,d\}$. For simplicity, we assume that all actions are feasible in all states. The probability transition kernel $P$ specifies the probability $p_a(s,s')$ of transitioning from state $s$ to state $s'$ under the action $a$. We denote the reward obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.\par

@@

where $\alpha \in (0,1)$ is a given discount factor. Here $J_u(s)$ is known as the value of the state $s$ under the SDP $u$, and the vector quantity $J_u\stackrel{\Delta}{=}(J_u(s), \forall s\in S)\in R^n$ is called the value-function corresponding to the SDP $u$. The \emph{optimal policy} $u^*$ is obtained as $u^*(s)\stackrel{\Delta}{=}\arg\max_{u\in U}J_u(s)$\footnote{Such $u^*$ exists and is well defined in the case of infinite horizon discounted reward MDP, for more details see \cite{Puter}.}, where $U$ is the class of all SDPs. The \emph{optimal value-function} $J^*$ is the one obtained under the optimal policy, i.e., $J^*=J_{u^*}$.The optimal value function $J^*$ can be obtained by solving the following linear program :

@@

\text{s.t.}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'), s\in S, a \in A.\nn

@@

and the optimal policy can be obtained as 
u^*(s)=\arg\max_{ a\in A}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big)

@@

We now define certain important quantities which will used in the rest of the discussion.

@@

@@

When the MDP has a large number of states it is difficult to solve for $J^*$, using either the linear program \eqref{mdplp} or other full state representation methods such as value iteration, policy iteration \cite{BertB}).

### 2016-07-08 single/num.tex
Chandru's shortened version

In this section, we show via an example in the domain of controlled queues \cite{ALP}  that the error term $\et$ indicates the quality of the constraint approximation. The queuing model used here is similar to the one in Section~$5.2$ of \cite{ALP}. We consider a single queue with arrivals and departures. The state of the system is the queue length with the state space given by $S=\{0,\ldots,n-1\}$, where $n-1$ is the buffer size of the queue. The action set $A=\{1,\ldots,d\}$ is related to the service rates. We let $s_t$ denote the state at time $t$. The state at time $t+1$ when action $a_t \in A $ is chosen is given by $s_{t+1}= s_{t}+1$ with probability $p$, $s_{t+1}= s_{t}-1$ with probability $q(a_t)$ and $s_{t+1}= s_t$, with probability $(1-p-q(a_t))$. For states $s_t=0$ and $s_t=n-1$, the system dynamics is given by 	$s_{t+1}= s_{t}+1$ with probability $p$ when $s_t=0$ and $s_{t+1}=s_t-1$ with probability $q(a_t)$ when $s_t=n-1$. The service rates satisfy $0<q(1)\leq \ldots\leq q(d)<1$ with $q(d)>p$ so as to ensure `stabilizability' of the queue. The reward associated with the action $a \in A$ in state $s\in S$ is given by $g_a(s)=-(s+60q(a)^3)$. We made use of polynomial features in $\Phi$ (i.e., $1,s,\ldots,s^{k-1}$) since they are known to work well for this domain \cite{ALP}.
For our experiments, we chose two contenders for the $W$-matrix and compared them with random positive matrix $W_r$. Our choices of the $W$ matrix were: {$\mathbf{(i)}$} $W_c$- matrix that corresponds to sampling according to $c$. This is justified by the insights obtained from Theorem~\ref{st} on the error term $\et$, i.e., the idea of selecting the important states. {$\mathbf{(ii)}$} $W_a$ state-aggregation matrix, a heuristic derived using the fact that $\lambda^*$ is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$. Our choice of the $W_a$ matrix to correspond to aggregation of near by states is motivated by the observation that $P^n$ captures $n^{th}$ hop connectivity/neighborhood information. 

@@

W_a(i,j)&=1, \mb\text{for all } j\mb\text{s.t.}\mb \nn\\&j=(i-1)\times\frac{n}{m}+k+(l-1)\times n, \nn\\&\mb\quad\quad k=1,\ldots,\frac{n}{m}, l=1,\ldots,d,\nn\\

@@

We ran our experiments on a moderately large queuing system denoted by $Q_L$ with $n=10^4$ and $d=4$ with $q(1)=0.2$, $q(2)=0.4$, $q(3)=0.6$, $q(4)=0.8$, $p=0.4$ and $\alpha=0.98$. We chose $k=4$ (i.e., we used $1, s,s^2$ and $s^3$ as basis vectors) and we chose $W_a$ \eqref{wdes}, $W_c$, $W_i$ and $W_r$ with $m=50$. We set $c(s)=(1-\zeta) \zeta^s$, where $s=1,\ldots,9999$, with $\zeta=0.9$ and $\zeta=0.999$ respectively. The results in Table~\ref{pref} show that the performance exhibited by $W_a$ and $W_c$ is better by several orders of magnitude over `random' in the case of the large system $Q_L$ and is closer to the ideal sampler $W_i$. Note that computing $\et$ was hard in the case of large $n=10^4$ and since $\et$ is completely dependent on the structure of $\Phi$, $T$ and $W$ we instead computed the same for $n=10$ and used it as a surrogate. Accordingly, we chose a smaller system $Q_S$ with $n=10$, $d=2$, $k=2$, $m=5$, $q(1)=0.2$, $q(2)=0.4$, $p=0.2$ and $\alpha=0.98$. Note that a better performance of $W_a$ and $W_c$ is in agreement with a lower value of $\et$.

@@

\resizebox{\columnwidth}{!}{

@@

$\et$ & $0$&	$39$& $24$& $214$ \\\hline

@@

}

@@

\begin{comment}

@@

\begin{tabular}{|c|c|c|c|}\hline
Performance Metric&	$W_i$&	$W_c$& $W_a$ \\\hline
$||J_{\hu}||_{1,c}$ for $\zeta=0.9$& $-441.25$&	$-450.59$& $-446.49$ \\\hline
$||J_{\hu}||_{1,c}$ for $\zeta=0.999$& $-2.0611e+04$&	$-2.0611e+04$& $-2.0612e+04$ \\\hline
\caption{Shows performance metrics for $Q_L$. Here $||J^*||_{1,c}=-439.26$ for $\zeta=0.9$ and $||J^*||_{1,c}=-2.0603e+04$ for $\zeta=0.999$   and a random policy yields a total reward of $-1.2661e+03
$.}
\end{comment}

>>>>

In this section, we show via an example in the domain of controlled queues \cite{ALP}  that the error term $||J^*-\Gamma J^* ||_\infty$ indicates the quality of the constraint approximation. The queuing model used here is similar to the one in Section~$5.2$ of \cite{ALP}. We consider a single queue with arrivals and departures. The state of the system is the queue length with the state space given by $S=\{0,\ldots,n-1\}$, where $n-1$ is the buffer size of the queue. The action set $A=\{1,\ldots,d\}$ is related to the service rates. We let $s_t$ denote the state at time $t$. The state at time $t+1$ when action $a_t \in A $ is chosen is given by $s_{t+1}= s_{t}+1$ with probability $p$, $s_{t+1}= s_{t}-1$ with probability $q(a_t)$ and $s_{t+1}= s_t$, with probability $(1-p-q(a_t))$. For states $s_t=0$ and $s_t=n-1$, the system dynamics is given by 	$s_{t+1}= s_{t}+1$ with probability $p$ when $s_t=0$ and $s_{t+1}=s_t-1$ with probability $q(a_t)$ when $s_t=n-1$. The service rates satisfy $0<q(1)\leq \ldots\leq q(d)<1$ with $q(d)>p$ so as to ensure `stabilizability' of the queue. The reward associated with the action $a \in A$ in state $s\in S$ is given by $g_a(s)=-(s+60q(a)^3)$. We made use of polynomial features in $\Phi$ (i.e., $1,s,\ldots,s^{k-1}$) since they are known to work well for this domain \cite{ALP}.
For our experiments, we choose two contenders for the $W$-matrix and compare them with random positive matrix $W_r$. Our choices of the $W$ matrix are as below.{$\mathbf{(i)}$} $W_c$- matrix that corresponds to sampling according to $c$. This is justified by the insights obtained from Theorem~\ref{st} on the error term $\et$, i.e., the idea of selecting the important states. {$\mathbf{(ii)}$} $W_a$ state-aggregation matrix, a heuristic derived using the fact that $\lambda^*$ is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$. Our choice of the $W_a$ matrix to correspond to aggregation of near by states is motivated by the observation that $P^n$ captures $n^{th}$ hop connectivity/neighborhood information. 

@@

W_a(i,j)&=1, \mb\text{for all } j\mb\text{s.t.}\mb j=(i-1)\times\frac{n}{m}+k+(l-1)\times n, \nn\\&\mb\quad\quad k=1,\ldots,\frac{n}{m}, l=1,\ldots,d,\nn\\

@@

We ran our experiments on a moderately large queuing system denoted by $Q_L$ with $n=10^4$ and $d=4$ with $q(1)=0.2$, $q(2)=0.4$, $q(3)=0.6$, $q(4)=0.8$, $p=0.4$ and $\alpha=0.98$. We chose $k=4$ (i.e., we used $1, s,s^2$ and $s^3$ as basis vectors) and we chose $W_a$ \eqref{wdes}, $W_c$, $W_i$ and $W_r$ with $m=50$. We set $c(s)=(1-\zeta) \zeta^s$, where $s=1,\ldots,9999$, with $\zeta=0.9$ and $\zeta=0.999$ respectively. The results in Table~\ref{pref} show that the performance exhibited by $W_a$ and $W_c$ is better by several orders of magnitude over `random' in the case of the large system $Q_L$ and is closer to the ideal sampler $W_i$.

@@

@@

$||\Gamma J^*-\hg J^*||_\infty$ & $0$&	$39$& $24$& $214$ \\\hline

@@

@@

@@

\begin{comment}
\FloatBarrier
\begin{table}[H]
%\resizebox{\columnwidth}{!}{
\begin{center}
\begin{tabular}{|c|c|c|c|}\hline
Performance Metric&	$W_i$&	$W_c$& $W_a$ \\\hline
$||J_{\hu}||_{1,c}$ for $\zeta=0.9$& $-441.25$&	$-450.59$& $-446.49$ \\\hline
$||J_{\hu}||_{1,c}$ for $\zeta=0.999$& $-2.0611e+04$&	$-2.0611e+04$& $-2.0612e+04$ \\\hline
\end{tabular}
\end{center}
%}
\caption{Shows performance metrics for $Q_L$. Here $||J^*||_{1,c}=-439.26$ for $\zeta=0.9$ and $||J^*||_{1,c}=-2.0603e+04$ for $\zeta=0.999$   and a random policy yields a total reward of $-1.2661e+03
$.}
\label{pref}
\end{table}
\end{comment}
